\textsc{Second-order state-constraint Hamilton-Jacobi equations}

### 2021-01-27 Drafts and notes/Old_draft_03.tex
Added Construction

\subsection{Convergence result}
Assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$. Assume that $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$.

Let $u^\varepsilon$ be the solution to \eqref{eq:PDE}, we observe that if $u^\varepsilon\rightarrow u^0$ uniformly on compact subsets of $\Omega$, we see that $u(x)\rightarrow +\infty$ as $\mathrm{dist}(x,\partial \Omega)\to 0$ as well, therefore the limiting solution is not the state-constraint solution to a limiting first order equation.

@@

\begin{thm}[Qualitative result] Assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$. Assume that $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$. Let $u^\varepsilon$ be the solution to \eqref{eq:PDE}, then $u^\varepsilon \rightarrow u^0$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$ and $u^0$ solves
\begin{equation}\label{eq:PDE0}
    \begin{cases}
    \lambda u(x) + |Du(x)|^p - f(x)=  0 \qquad\text{in}\;\Omega, \vspace{0cm}\\
    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u^0(x) = +\infty.
    \end{cases} \tag{PDE$_0$}
\end{equation}
\end{thm}

\color{blue}
\begin{proof} (\textit{Added on Jan 16, 2021 - Heuristic idea}) Assume that we can get some sort of equi-continuity of the family $\{u^\varepsilon\}_{\varepsilon>0}$ in a local way, that is, for any compact sub-domain $\Omega'\subset\subset \Omega$ there is a constant $C(\Omega')$ such that
\begin{equation}\label{eq:bound}
    \Vert u^\varepsilon\Vert_{L^\infty(\Omega')} +\Vert Du^\varepsilon\Vert_{L^\infty(\Omega')} \leq C(\Omega').
\end{equation}
This should be done using Berstein's method (fill in later, and as $u$ blows up on $\partial \Omega$, this bound \eqref{eq:bound} may not be improved). Now let us assume via some subsequence $\varepsilon_j\to 0$ we have $u^{\varepsilon_j}\rightarrow u^0$ uniformly on compact subsets of $\Omega$, the interior stability of viscosity solution should yield us that 
\begin{equation*}
    \lambda u^0(x) + |Du^0(x)|^p - f(x) = 0 \qquad\text{in}\;\Omega.
\end{equation*}
The real difficulty is describing what is the behavior of $u^0$ on the boundary. It is clear that
\begin{equation*}
    \displaystyle  \lim_{\mathrm{dist}(x,\partial \Omega)\to 0} u^0(x) = +\infty.
\end{equation*}

In fact, for each $x_0\in \partial \Omega$, let $\Vec{\mathfrak{n}}(x_0)$ be the unit outward normal vector, consider $x_s = x_0 - s\Vec{\mathfrak{n}}(x_0)$ for $s>0$. For each $j\in \mathbb{N}$ there holds $\lim_{s\to 0} u^\varepsilon(x_s) = +\infty$, therefore we can find a subsequence $s_j \to 0$ such that 
\begin{equation*}
    u^\varepsilon(x_{s_j}) \geq \tfrac{1}{\varepsilon_j}.
\end{equation*}
\vspace{2cm}

As we expect it to solves \eqref{eq:PDE0}, it should be the maximal subsolution (hence, solution) to 
\begin{equation}\label{eq:S_lambda}
    \lambda u(x) + |Du(x)|^p - f(x) = 0 \qquad\text{in}\;\Omega.
\end{equation}
Let $v^\varepsilon\in \rmC^2(\Omega)\cap \rmC(\overline{\Omega})$ be the unique solution to the Dirichlet problem
\begin{equation}\label{eq:v_eps}
\begin{cases}
    \lambda v^\varepsilon(x) + |Dv^\varepsilon(x)|^p - f(x) = \varepsilon \Delta v^\varepsilon(x) &\qquad\text{in}\;\Omega,\\
    \;\;\,\quad\quad\qquad\qquad\qquad\qquad v^\varepsilon = u &\qquad \text{on}\;\partial\Omega.
\end{cases}
\end{equation}
where $u\in \rmC(\overline{\Omega})$ is the unique solution of \eqref{eq:PDE0}. Note that $v^\varepsilon\rightarrow v^0$ solves the corresponding Dirichlet problem
\begin{equation}\label{eq:v_0}
\begin{cases}
    \lambda v^0(x) + |Dv^0(x)|^p - f(x) = 0 &\qquad\text{in}\;\Omega,\\
    \;\;\,\quad\quad\qquad\qquad\qquad\qquad v^0 = u &\qquad \text{on}\;\partial\Omega.
\end{cases}
\end{equation}
\begin{lem} $v^0\equiv u$ as the unique solution to \eqref{eq:PDE0}.
\end{lem}
\begin{proof} We observe that $u$ solves \eqref{eq:PDE0} is the unique solution to the Dirichlet problem \eqref{eq:v_0} as well, thus $v^0 \equiv u$ by comparison principle.
\end{proof}
\noindent By comparison principle, we see that
\begin{equation*}
    v^\varepsilon(x)\leq u^\varepsilon(x) \qquad\text{for}\;x\in \Omega.
\end{equation*}
Let $\varepsilon\to 0$, we deduce that
\begin{equation*}
    u(x)\leq u^0(x) \qquad\text{for}\;x\in \Omega.
\end{equation*}
\end{proof}
\color{black}

\begin{lem} If $\delta$ is small enough then $u^0$ is a supersolution of \eqref{S_0} on $\overline{\Omega}_\delta$.
\end{lem}
\begin{proof} For $\delta>0$, let us denote $v_\delta\in\rmC(\overline{\Omega}_\delta)$ be the state-constraint viscosity subsolution to the problem $\lambda u(x) + H(x,Du(x)) = 0$ in $\Omega_\delta$, then by Lemma  \ref{lem:max} we have
\begin{equation}\label{eq:les1}
   u^0(x) \leq v_\delta(x) \qquad\text{for}\;x\in \overline{\Omega}_\delta
\end{equation}
since $u^0 \in \rmC(\overline{\Omega}_\delta)$ is a viscosity (sub)solution to $\lambda u(x) + H(x,Du(x)) = 0$ in $\Omega_\delta$. Let us denote $v^\varepsilon\in \rmC^2(\Omega_\delta)\cap \rmC(\overline{\Omega}_\delta)$ as the unique solution to the Dirichlet problem
\begin{equation}\label{eq:vv_eps}
\begin{cases}
    \lambda v^\varepsilon(x) + |Dv^\varepsilon(x)|^p - f(x) = \varepsilon \Delta v^\varepsilon(x) &\qquad\text{in}\;\Omega_\delta,\\
    \;\;\,\quad\quad\qquad\qquad\qquad\qquad v^\varepsilon = v_\delta &\qquad \text{on}\;\partial\Omega_\delta.
\end{cases}
\end{equation}
Comparing $u^\varepsilon$ and $v^\varepsilon$ on $\overline{\Omega}_\delta$, for $\delta$ small enough we have $v_\delta\leq u^\varepsilon$ on $\partial \Omega_\delta$, thus by comparison principle for \eqref{eq:vv_eps} we obtain that $v^\varepsilon \leq u^\varepsilon$ on $\overline{\Omega}_\delta$, thus as $\varepsilon\to 0$ we have
\begin{equation}\label{eq:les2}
    v_\delta(x) \leq u^0(x)  \qquad\text{for}\;x\in \overline{\Omega}_\delta.
\end{equation}
From \eqref{eq:les1} and \eqref{eq:les2} we deduce that $v_\delta = u^0$ on $\overline{\Omega}_\delta$.
\end{proof}

@@

To find candidate for subsolution and supersolution to \eqref{eq:PDE}, we use the ansatz
\begin{equation}\label{eq:ansatz}
    u(x) = C_0 d(x)^{-\alpha}, \qquad x\in \Omega
\end{equation}
as we expect it blows up near the boundary like some thing proportionate to inverse of the distance function, due to the structure of $H(x,\varrho) = |\varrho|^p - f(x)$. Let us plug \eqref{eq:ansatz} into \eqref{eq:PDE} we obtain that the highest order terms are
\begin{equation*}
        -C_0 \alpha(\alpha+1)d^{-(\alpha+2)} + C_0^p \alpha^p d^{-(\alpha+1)p}.
\end{equation*}
Setting them to zero, we deduce that
\begin{equation*}
    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_0 = \frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}.
\end{equation*}
We can obtain the following families of subsolution on $\Omega^\delta$ and supersolution on $\Omega^\delta$ as follow.
\begin{equation*}
        \overline{w}_{\eta,\delta}(x) = \frac{C_0+\eta}{(d(x)-\delta)^\alpha} +\frac{C_\eta}{\lambda} \quad\text{for}\;x\in \Omega_\delta \qquad\text{and}\qquad \underline{w}_{\eta,\delta}(x) = \frac{C_0-\eta}{(d(x)+\delta)^\alpha} -\frac{C_\eta}{\lambda} \quad\text{for}\;x\in \Omega^\delta.
\end{equation*}
We divide the rest of the proof into 3 steps.
\begin{itemize}
    \item Step 1. Building a maximal solution to \eqref{eq:PDE}. 
\end{itemize}
\end{proof}

@@

\section{Differentiability with respect to the parameter}
For the vanishing viscosity problem with the Dirichlet boundary condition,
\begin{equation}
\label{dir}
\left\{
  \begin{aligned}
    H(x, Du^\epsilon(x)) &= \epsilon \Delta u^\epsilon \quad \, \text{in } U, \\
              u^\epsilon &= 0 \quad \qquad \text{on } \partial U,
  \end{aligned}
\right.
\end{equation}
we want to show the smooth dependence of $u^\epsilon$ on $\epsilon$.
Formally, if we differentiate \eqref{dir} with respect to $\epsilon$, we get
\begin{equation}
\label{dir_dif}
\left\{
  \begin{aligned}
    D_pH(x, Du^\epsilon(x))\cdot Du^\epsilon_\epsilon &= \epsilon \Delta u^\epsilon_\epsilon +\Delta u^\epsilon \quad \, \text{in } U, \\
              u^\epsilon_\epsilon &= 0 \quad \qquad  \qquad  \text{on } \partial U.
  \end{aligned}
\right.
\end{equation}
By Schaefer's fixed point theorem and the maximal principle, $u^\epsilon_\epsilon$ is the unique solution in $C^2(\overline{U})$ of \eqref{dir_dif} \textcolor{orange}{(needs double check)}. The main idea is, we look at the difference quotients $\displaystyle \frac{u^{\epsilon+h}-u^\epsilon}{h}$and prove that as $h \to 0^+$, they converge to a limiting function $w^{\ast}$ in the uniform norm \textcolor{orange}{(maybe weaker convergence is fine)} such that $w^{\ast}$ solves \eqref{dir_dif}. Since \eqref{dir_dif} has a unique solution, we have $$u^\epsilon_\epsilon=\lim_{h \to 0^+}\frac{u^{\epsilon+h}-u^\epsilon}{h}.$$

Fix $\epsilon >0$. Let $$w^h(x):=\frac{u^{\epsilon+h}(x)-u^\epsilon(x)}{h} \in C^2(\overline{U}).$$

A little computation will show that $w^h$ solves

\begin{equation}
\label{dir_quo}
\left\{
  \begin{aligned}
   \epsilon \Delta w^h(x) + \frac{\epsilon}{\epsilon + h}\Delta u^\epsilon &= \frac{\epsilon}{\epsilon +h} \int_0^1 D_pH(x, Du^\epsilon+\theta (Du^{\epsilon+h}-Du^\epsilon)) d\theta \cdot Dw^h \quad \, \text{in } U, \\
              w^h &= 0 \quad \qquad \text{on } \partial U.
  \end{aligned}
\right.
\end{equation}
Heuristically, we see as $h \to 0^+$, \eqref{dir_quo} "converges" to \eqref{dir_dif}.

\textcolor{orange}{Still thinking about how to show $w^h$ converges uniformly as $h \to 0^+$. I am tring to show $\| w^h-w^\ast\|_\infty \to 0$ by looking at the equation solved by $v^h:=w^h-w^\ast$. More to fill in...}

>>>>

\subsection{Convergence result}
Assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$. Assume that $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$. \vspace{0.2cm}

\color{blue} 
\paragraph{\underline{\textbf{Double check! Contradiction appears!}}} Let $u^\varepsilon$ be the solution to \eqref{eq:PDE}, we observe that if $u^\varepsilon\rightarrow u^0$ uniformly on compact subsets of $\Omega$, we see that $u(x)\rightarrow +\infty$ as $\mathrm{dist}(x,\partial \Omega)\to 0$ as well, therefore the limiting solution is not the state-constraint solution to a limiting first order equation.
\color{black}

@@

\begin{lem} Assume $u^{\varepsilon_j}\rightarrow u^0$ locally uniformly and let $w\in \rmC(\overline{\Omega})$ be the unique solution to 
\begin{equation*}
    \begin{cases}
    \lambda w(x)  + H(x,Dw(x)) \leq 0 \qquad\text{in}\;\Omega,\\
    \lambda w(x)  + H(x,Dw(x)) \geq 0 \qquad\text{on}\;\overline{\Omega}.
    \end{cases}
\end{equation*}
We have $u^0(x)\geq u(x)$ for $x\in \Omega$.
\end{lem}
\begin{proof} For $\delta>0$, let $\Omega_\delta = \{x\in \Omega: \mathrm{dist}(x,\Omega) < \delta\}$ and $v_\delta\in\rmC(\overline{\Omega}_\delta)$ be the state-constraint viscosity subsolution to the problem $\lambda u(x) + H(x,Du(x)) = 0$ in $\Omega_\delta$.% If $\delta$ is small enough then $u^0$ is a supersolution of \eqref{S_0} on $\overline{\Omega}_\delta$.

As $v_\delta\rightarrow w$ locally uniformly as $\delta\rightarrow 0^+$ and $w$ is bounded, we see that $v_\delta$ is uniformly bounded. Let $v^\varepsilon\in \rmC^2(\Omega_\delta)\cap \rmC(\overline{\Omega}_\delta)$ be the unique solution to the Dirichlet problem
\begin{equation}\label{eq:vv_eps}
\begin{cases}
    \lambda v^\varepsilon(x) + |Dv^\varepsilon(x)|^p - f(x) = \varepsilon \Delta v^\varepsilon(x) &\qquad\text{in}\;\Omega_\delta,\\
    \;\;\,\quad\quad\qquad\qquad\qquad\qquad v^\varepsilon = v_\delta &\qquad \text{on}\;\partial\Omega_\delta.
\end{cases}
\end{equation}
Since $v_\delta$ is bounded, for all $\delta$ small enough $v_\delta\leq u^\varepsilon$ on $\partial \Omega_\delta$, thus by maximum principle $v^\varepsilon \leq u^\varepsilon$ on $\overline{\Omega}_\delta$, hence as $\varepsilon\to 0$ we have
\begin{equation}\label{eq:les2}
    v_\delta(x) \leq u^0(x)  \qquad\text{for}\;x\in \overline{\Omega}_\delta.
\end{equation}
Let $\delta\rightarrow 0$ we obtain the conclusion $w(x)\leq u^0(x)$ for $x\in \Omega$.
\end{proof}

\begin{thm}[Qualitative result] Assume $\Omega$ is an open, bounded and connected with $\mathrm{C}^2$ boundary domain of $\mathbb{R}^n$. Assume that $f\in \mathrm{C}(\overline{\Omega})\cap W^{1,\infty}(\Omega)$ and $1<p<2$. Let $u^\varepsilon$ be the solution to \eqref{eq:PDE}, then $u^\varepsilon \rightarrow u^0$ locally uniformly in $\Omega$ as $\varepsilon\rightarrow 0$ and $u^0$ solves
\begin{equation}\label{eq:PDE0}
    \begin{cases}
    \lambda u^0(x) + |Du^0(x)|^p - f(x)\leq  0 \qquad\text{in}\;\Omega, \\
    \lambda u^0(x) + |Du^0(x)|^p - f(x)\geq  0 \qquad\text{on}\;\overline{\Omega}.
    \end{cases}
\end{equation}
\end{thm}

@@

\noindent To find candidate for subsolution and supersolution to \eqref{eq:PDE}, we use the ansatz
\begin{equation}\label{eq:ansatz}
    u(x) = C_0 d(x)^{-\alpha}, \qquad x\in \Omega
\end{equation}
as we expect it blows up near the boundary like some thing proportionate to inverse of the distance function, due to the structure of $H(x,\varrho) = |\varrho|^p - f(x)$. Let us plug \eqref{eq:ansatz} into \eqref{eq:PDE} we obtain that the highest order terms are
\begin{equation*}
        -C_0 \alpha(\alpha+1)d^{-(\alpha+2)} + C_0^p \alpha^p d^{-(\alpha+1)p}.
\end{equation*}
Setting them to zero, we deduce that
\begin{equation*}
    \displaystyle\alpha = \frac{2-p}{p-1} \qquad\text{and}\qquad C_0 = \frac{1}{\alpha}(\alpha+1)^\frac{1}{p-1}.
\end{equation*}
We can obtain the following families of subsolution on $\Omega^\delta$ and supersolution on $\Omega^\delta$ as follow.
\begin{equation*}
        \overline{w}_{\eta,\delta}(x) = \frac{C_0+\eta}{(d(x)-\delta)^\alpha} +\frac{C_\eta}{\lambda} \quad\text{for}\;x\in \Omega_\delta \qquad\text{and}\qquad \underline{w}_{\eta,\delta}(x) = \frac{C_0-\eta}{(d(x)+\delta)^\alpha} -\frac{C_\eta}{\lambda} \quad\text{for}\;x\in \Omega^\delta.
\end{equation*}
We divide the rest of the proof into 3 steps.
\begin{itemize}
    \item Step 1. Building a maximal solution to \eqref{eq:PDE}. 
\end{itemize}
\end{proof}

@@

\section{Differentiability with respect to the parameter}
For the vanishing viscosity problem with the Dirichlet boundary condition,
\begin{equation}
\label{dir}
\left\{
  \begin{aligned}
    H(x, Du^\epsilon(x)) &= \epsilon \Delta u^\epsilon \quad \, \text{in } U, \\
              u^\epsilon &= 0 \quad \qquad \text{on } \partial U,
  \end{aligned}
\right.
\end{equation}
where  $H(x,p)$ is $C^\infty(\overline{U}\times \mathbb{R}^n)$, $\displaystyle \frac{H(x,p)}{|p|} \to \infty$ uniformly in $x$ as $|p| \to \infty$ and $\displaystyle \sup_{x\in U}|D_xH(x,p)|\leq C(1+|p|)$, we want to show the smooth dependence of $u^\epsilon$ on $\epsilon$.
Formally, if we differentiate \eqref{dir} with respect to $\epsilon$, we get
\begin{equation}
\label{dir_dif}
\left\{
  \begin{aligned}
    D_pH(x, Du^\epsilon(x))\cdot Du^\epsilon_\epsilon &= \epsilon \Delta u^\epsilon_\epsilon +\Delta u^\epsilon \quad \, \text{in } U, \\
              u^\epsilon_\epsilon &= 0 \quad \qquad  \qquad  \text{on } \partial U.
  \end{aligned}
\right.
\end{equation}
By Schaefer's fixed point theorem and the maximal principle, $u^\epsilon_\epsilon$ is the unique solution in $C^{2,\alpha}(\overline{U})$ of \eqref{dir_dif}.

The main idea is, we look at the difference quotients $\displaystyle \frac{u^{\epsilon+h}-u^\epsilon}{h}$and prove that as $h \to 0^+$, they converge to a limiting function $w^{\ast}$ in the uniform norm  such that $w^{\ast}$ solves \eqref{dir_dif}. Since \eqref{dir_dif} has a unique solution, we have $$u^\epsilon_\epsilon=\lim_{h \to 0^+}\frac{u^{\epsilon+h}-u^\epsilon}{h}.$$

\subsection{Solution $u^\epsilon \in C^{2,\alpha}(\overline{U})$ exists}
We use Schaufer's fixed point theorem as follows.

\begin{thm}
Suppose $X$ is a Banach space. Let $A:X \to X$ be continuous and compact. Assume the set $\{u\in X : u=\lambda A[u]$ for some $0 \leq  \lambda \leq 1\}$ is bounded. Then $A$ has a fixed point $u =A[u]$.
\end{thm}

Fix $0<\alpha<1$. Let $X=C^{1,\alpha}(\overline{U})$. Given $u \in X=C^{1,\alpha}(\overline{U})$, we look at the linear PDE
\begin{equation}
\label{fix}
\left\{
  \begin{aligned}
   \epsilon \Delta v &= H(x, Du) \quad \, \text{in } U, \\
              v &= 0 \qquad \qquad \text{on } \partial U.
  \end{aligned}
\right.
\end{equation}

Estimate the Holder norm of RHS
$$\|H(x, Du)\|_{C^{0, \alpha}(\overline{U})}:=\sup_{x\in\overline{U}} |H(x,Du(x))| + \sup_{x, y \in \overline{U}}\frac{|H(x, Du(x))-H(y, Du(y))|}{|x-y|^\alpha}.$$
Since $Du$ is bounded and H is smooth,
\begin{equation}
    \sup_{x\in\overline{U}} |H(x,Du(x))| \leq C.
\end{equation}

\begin{equation}
    \begin{aligned}
  &\sup_{x, y \in \overline{U}}\frac{|H(x, Du(x))-H(y, Du(y))|}{|x-y|^\alpha}\\
  \leq &  \sup_{x, y \in \overline{U}}\frac{|H(x, Du(x))-H(y, Du(x))|}{|x-y|^\alpha} + \sup_{x, y \in \overline{U}}\frac{|H(y, Du(x))-H(y, Du(y))|}{|x-y|^\alpha} \\
  =&    \sup_{x, y \in \overline{U}}\frac{|\int_0^1D_xH(y+\theta (x-y), Du(x))d\theta \cdot (x-y)|}{|x-y|^\alpha}\\& +
     \sup_{x, y \in \overline{U}}\frac{|\int_0^1D_pH(y, Du(y)+\theta (Du(x)-Du(y)))d\theta \cdot (Du(x)-Du(y))|}{|x-y|^\alpha}\\
  \leq &  C\sup_{x, y \in \overline{U}} (1+|Du(x)|)|x-y|^{1-\alpha} +  C \sup_{x, y \in \overline{U}}\frac{| (Du(x)-Du(y))|}{|x-y|^\alpha}\\
 \leq & C(1 + \|u\|_{C^{1,\alpha}(\overline{U})})
    \end{aligned}
\end{equation}
since $Du$ is bounded on $\overline{U}$, $D_pH \in C^\infty (\overline{U} \times \mathbb{R}^n)$ and
$\displaystyle \sup_{x\in U}|D_xH(x,p)|\leq C(1+|p|)$.

Therefore,
\begin{equation}
 \|H(x, Du)\|_{C^{0, \alpha}(\overline{U})} \leq C(1 + \|u\|_{C^{1,\alpha}(\overline{U})}).
\end{equation}
By Schauder estimates, there exists a unique solution $v \in C^{2,\alpha }(\overline{U})$ such that

\begin{equation}
\label{schauder}
    \|v\|_{C^{2, \alpha}(\overline{U})} \leq C  \|H(x, Du)\|_{C^{0, \alpha}(\overline{U})}. 
\end{equation}

Define operator $A$ on $X := C^{1, \alpha} (\overline{U}) $ by $A[u]=v$.

So 
\begin{equation}
     \|A[u]\|_{C^{2, \alpha}(\overline{U})} \leq C(1 + \|u\|_{C^{1,\alpha}(\overline{U})}),
\end{equation}

 and thus $A$ is continuous and compact. (i.e., if $\{u_k\}_{k=1}^\infty$ is bounded in $X=C^{1, \alpha}(\overline{U})$, then $\{A[u_k]\}_{k=1}\infty$ is bounded in $C^{2,\alpha} (\overline{U})$, thus precompact in $C^{1, \alpha}(\overline{U})$. Lemma 6.33 in Gilbarg and Trudinger. )

 Next we try to bound $\{u\in X : u=\lambda A[u]$ for some $0 \leq  \lambda \leq 1\}$.
 If $u=\lambda A[u]$, the PDE becomes

\begin{equation}
\label{lamb}
\left\{
  \begin{aligned}
   \epsilon \Delta u &= \lambda H(x, Du) \quad \, \text{in } U, \\
              u &= 0 \qquad \qquad \text{on } \partial U.
  \end{aligned}
\right.
\end{equation}

Calderon-Zygmund estimates tell us that if we have
\begin{equation}
\label{cald}
\left\{
  \begin{aligned}
  - \Delta v &=\Tilde{f}   \qquad \, \text{in } U, \\
              v &= 0 \qquad \text{on } \partial U.
  \end{aligned}
\right.
\end{equation}

and $\Tilde{f} \in {L^p(U)}$ for some $p\in (1, \infty)$, then $v \in W^{2,p}(U)$ and $$\|v\|_{w^{2,p}(U)} \leq C\|\Tilde{f}\|_{L^p(U)}.$$

Apply to \eqref{lamb} and we get

\begin{equation}
    \|u\|_{w^{2,p}(U)} \leq C\|H(x, Du)\|_{L^p(U)}
\end{equation}
\textcolor{red}{(I want RHS to be bounded by some constant so that I can choose $p$ larger than $n$ to  conclude $ \|u\|_{C^{1, \alpha}(U)} \leq   C\|u\|_{w^{2,p}(U)} \leq C$ by Morrey's estimate. But with the assumption on $H$, I don't really know how to bound RHS.)}

Choose $p=2n$ and $\displaystyle \alpha =\frac{1}{2}$. We have $\{u\in X : u=\lambda A[u]$ for some $0 \leq  \lambda \leq 1\}$ is bounded in $X= C^{1, \frac{1}{2}}(
\overline{U})$.
Thus Schaefer's fixed point theorem implies there exists a solution $u \in C^{2, \alpha}$ that solves \eqref{dir}.

\subsection{Smooth dependence on $\epsilon$}
Fix $\epsilon >0$. Let  $$w^h(x):=\frac{u^{\epsilon+h}(x)-u^\epsilon(x)}{h} \in C^{2,\alpha}(\overline{U}).$$

A little computation shows that $w^h$ solves

\begin{equation}
\label{dir_quo}
\left\{
  \begin{aligned}
   \epsilon \Delta w^h(x) + \frac{\epsilon}{\epsilon + h}\Delta u^\epsilon &= \frac{\epsilon}{\epsilon +h} \int_0^1 D_pH(x, Du^\epsilon+\theta (Du^{\epsilon+h}-Du^\epsilon)) d\theta \cdot Dw^h \quad \, \text{in } U, \\
              w^h &= 0 \quad \qquad \text{on } \partial U.
  \end{aligned}
\right.
\end{equation}
We want to bound $\{w^h\}_{h>0}$ in $C^{2, \alpha}(\overline{U})$ uniformly in $h$. (Then $\{w^h\}_{h>0}$ is precompact in  $C^{2, \gamma}(\overline{U})$ for $\gamma < \alpha$ and we can pass to limit.) Since the coefficients depend on $Du^{\epsilon+h}-Du^\epsilon$, in order to use Schauder/Calderon-Zygmond estimates, we need to bound the Holder norm of $Du^{\epsilon+h}-Du^\epsilon$ uniformly in h.

If we look at the equation $u^{\epsilon +h} -u^\epsilon$ solves, i.e.,
\begin{equation}
\label{diff}
\left\{
  \begin{aligned}
   \epsilon (\Delta u^{\epsilon+h}(x) -\Delta u^\epsilon(x) )+ h \Delta u^{\epsilon+h}&= \int_0^1 D_pH(x, Du^\epsilon+\theta (Du^{\epsilon+h}-Du^\epsilon)) d\theta \cdot D( u^{\epsilon+h}(x) - u^\epsilon(x)) \quad \, \text{in } U, \\
              w^h &= 0 \quad \qquad \text{on } \partial U.
  \end{aligned}
\right.
\end{equation}

\textcolor{red}{(Again the coeffients depend on $Du^{\epsilon+h}-Du^\epsilon$.I don't know how to use Schauder/Calderon-Zygmond estimates at this point...)}
